LOSA Fuel Poverty maps

### 2021-09-02 LSOA Fuel poverty.Rmd
Trying to resolve issue with age fuel poverty graph

# plotting the change in fuel poverty from 2018-2012 of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pc_diff)) +
  scale_fill_continuous(name = "Change in Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Winchester")
```
### Over 65 annd Fuel Poverty
```{r Loading in the Census age data}
inFile<-paste0(dataFolder, "census/KS102EW-age-categories.csv")
census_age<-readr::read_csv (inFile)
census_age$'LSOA11CD'<- census_age$'geography code'
head(census_age)
names(census_age)
```
```{r Mapping the fuel poverty in over 65s}
#census_age$"LSOA11CD" <- census_age$"geography code"
Census_age_fp <- merge(lsoa_fuelpov_2019, census_age, by = "LSOA11CD")
names(Census_age_fp)
census_age$oldpop <- Census_age_fp$'Over 65s'/Census_age_fp$'Age: All usual residents; measures: Value'
ggplot(Census_age_fp, aes(x=oldpop, y='Proportion of households fuel poor (%)')) +
  geom_point()

>>>>

# plotting the change in fuel poverty from 2018-2012 of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pc_diff)) +
  scale_fill_continuous(name = "Change in Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Winchester")
```
### Over 65 annd Fuel Poverty
```{r Loading in the Census age data}
inFile<-paste0(dataFolder, "census/KS102EW-age-categories.csv")
census_age<-readr::read_csv (inFile)
census_age$oldpop <- census_age$'Over 65s'/census_age$'Age: All usual residents; measures: Value'
census_age$'LSOA11CD'<- census_age$'geography code'
head(census_age)
names(census_age)
```
```{r Mapping the fuel poverty in over 65s}
#census_age$"LSOA11CD" <- census_age$"geography code"
Census_age_fp <- merge(lsoa_fuelpov_2019, census_age, by = "LSOA11CD")
names(Census_age_fp)
ggplot(Census_age_fp, aes(x=oldpop, y='Proportion of households fuel poor (%)')) +
  geom_point()
